Quantitative processing of broadband data as implemented in a scientific splitbeam echosounder

### 2022-03-22 Paper/Manuscript.tex
Split an overlong equation and highlighted comment
Tidy up a list

The discrete Fourier transforms of the target signal, $\ypctargetf(\samplesymf)$, and the reduced auto correlation signal, $\ymfautoredf(\samplesymf)$, are given by:
\begin{eqnarray}
\label{eq:DFT_Target_Auto}
\ypctargetf(\samplesymf) & = & \dft_\ndft(\ypctarget(\samplesymt)),\\
\ymfautoredf(\samplesymf) & = & \dft_\ndft(\ymfautored(\samplesymt)),
\end{eqnarray}
where $\dft$ indicates the Fourier transform of length $\ndft$ and $\samplesymf$ the sample index in the frequency domain.
The nomalized discrete Fourier transform of the target signal, $\ypctargetnormf(\samplesymf)$, (Fig. \ref{fi:TS}) is then calculated by: 
%
\begin{equation}
\label{eq:DFT_Target_Auto_Norm}
\ypctargetnormf(\samplesymf) = \frac{\ypctargetf(\samplesymf)} {\ymfautoredf(\samplesymf)}.
\end{equation}
%
\hl{The corresponding frequencies f\_m\_t (?) are calculate as follows... See the function EK80CalculationPaper.calcDFTforTS. Nils Olav did not quite get this so please enlighten me...}

@@

Volume backscattering samples compressed over the operational frequency band are estimated by applying Eq. \ref{eq:sv_f} to the received digitized power samples using the on-axis gain value with $f$ set to the centre frequency of the broadband pulse, $\fc$:
\begin{equation}
\label{eq:Sv}
\sv(\samplesymt)  =  10\log_{10}(\prxe(\samplesymt)) + 20\log_{10}(\range_c(\samplesymt)) + 2\absorp(\fc)\range_c(\samplesymt) 
- 10\log_{10}\left( \frac{\ptxe \wlen^2(\fc) \cw \teff \eqang(\fc) \gainzero^2(\fc)}{32\pi^2} \right),
\end{equation}
noting that $\sv(\samplesymt)$ is an average over frequency of all echoes received at sample $\samplesymt$. In this case, the time window, $\tslide$, is the effective pulse duration, $\teff$, resulting from pulse compression.

@@

In this implementation (ref code) several choices have been made. Some of these are well founded in signal processing literature whereas others are of a more practical and ad-hoc nature, where other approaches could been equally valid. These include, as examples,\\ 
How to handle calibration, interpolation, missing calibration\\
Transmit pulse\\
Tapering of the transmit pulse\\
Decimation factors and filters\\
When Convoling the recieved signal with the transmit pulse - edge cases\\
Assuemd four sector transducer\\
Matched load - hvor stor effekt å gå utover \\
Assumed an impedance (trancuder)\\
Effective pulse duration...\\
Assuming SED algorithm, know the target depth. Improvements possible (SED for broadband). Number of samples for pulse comp - what is included, dense aggregations, sidelobes - pc, ...\\
Window size\\
Edge cases - removed\\

>>>>

The discrete Fourier transforms of the target signal, $\ypctargetf(\samplesymf)$, and the reduced auto correlation signal, $\ymfautoredf(\samplesymf)$, are given by:
\begin{eqnarray}
\label{eq:DFT_Target_Auto}
\ypctargetf(\samplesymf) & = & \dft_\ndft(\ypctarget(\samplesymt)),\\
\ymfautoredf(\samplesymf) & = & \dft_\ndft(\ymfautored(\samplesymt)),
\end{eqnarray}
where $\dft$ indicates the Fourier transform of length $\ndft$ and $\samplesymf$ the sample index in the frequency domain.
The nomalized discrete Fourier transform of the target signal, $\ypctargetnormf(\samplesymf)$, (Fig. \ref{fi:TS}) is then calculated by: 
%
\begin{equation}
\label{eq:DFT_Target_Auto_Norm}
\ypctargetnormf(\samplesymf) = \frac{\ypctargetf(\samplesymf)} {\ymfautoredf(\samplesymf)}.
\end{equation}
%
\hl{The corresponding frequencies f\_m\_t (?) are calculate as follows...

See the function EK80CalculationPaper.calcDFTforTS. Nils Olav did not quite get this so please enlighten me...}

@@

Volume backscattering samples compressed over the operational frequency band are estimated by applying Eq. \ref{eq:sv_f} to the received digitized power samples using the on-axis gain value with $f$ set to the centre frequency of the broadband pulse, $\fc$:
\begin{equation}
\label{eq:Sv}
\begin{split}
\sv(\samplesymt)  =  10\log_{10}(\prxe(\samplesymt)) + 20\log_{10}(\range_c(\samplesymt)) + 2\absorp(\fc)\range_c(\samplesymt) \\
- 10\log_{10}\left( \frac{\ptxe \wlen^2(\fc) \cw \teff \eqang(\fc) \gainzero^2(\fc)}{32\pi^2} \right),
\end{split}
\end{equation}
noting that $\sv(\samplesymt)$ is an average over frequency of all echoes received at sample $\samplesymt$. In this case, the time window, $\tslide$, is the effective pulse duration, $\teff$, resulting from pulse compression.

@@

In this implementation (ref code) several choices have been made. Some of these are well founded in signal processing literature whereas others are of a more practical and ad-hoc nature, where other approaches could been equally valid. These include, as examples,
\begin{itemize}
\item How to handle calibration, interpolation, missing calibration
\item Transmit pulse
\item Tapering of the transmit pulse
\item Decimation factors and filters
\item When Convoling the recieved signal with the transmit pulse - edge cases
\item Assuemd four sector transducer
\item Matched load - hvor stor effekt å gå utover 
\item Assumed an impedance (trancuder)
\item Effective pulse duration...
\item Assuming SED algorithm, know the target depth. Improvements possible (SED for broadband). Number of samples for pulse comp - what is included, dense aggregations, sidelobes - pc, ...
\item Window size
\item Edge cases - removed
\end{itemize}
